Climate efficiency

### 2021-12-23 Paper.Rmd
Added the map of the US with covered counties in the climate data

@@

@@

unique(countyData[,c('COUNTY_ANSI','COMMODITY_DESC')])

@@

@@

<!-- ```{r echo = FALSE} -->

<!-- countiesOnMap = maps::map('county',plot=FALSE) -->

<!-- countiesWithPreciptiation = maps::county.fips[maps::county.fips$fips %in% unique(precipitationMonthly$FIPS),] -->

<!-- countiesOnMap$col = ifelse(countiesOnMap$names %in% countiesWithPreciptiation$polyname,'blue','white') -->

<!-- maps::map('county',plot=TRUE, col = countiesOnMap$col, fill = TRUE) -->

<!-- ``` -->

>>>>

# Introduction

# Data

$$ y_t  = \alpha_0 + \alpha_1 y_t$$
where ${{\alpha }_{1}}$ is the county yield intercept, $f\left( t \right)$ is the county’s estimated yield trend through time and ${{\varepsilon }_{t}}$ is the county’s residual yield variation. The following set of linear or nonlinear functional form of $f\left( t \right)$ is evaluated:

## Crops data

We obtained the crops data...

@@

### Detrending crops data

@@

#unique(countyData[,c('COUNTY_ANSI','COMMODITY_DESC')])

@@

## Climate data

@@

```{r echo = FALSE, fig.cap='Counties covered by climate data'}

countiesOnMap = maps::map('county',plot=FALSE)

countiesWithPreciptiation = maps::county.fips[maps::county.fips$fips %in% unique(precipitationMonthly$FIPS),]

countiesOnMap$col = ifelse(countiesOnMap$names %in% countiesWithPreciptiation$polyname,'blue','white')

maps::map('county',plot=TRUE, col = countiesOnMap$col, fill = TRUE)
